Algomusicology, ????, Profit

### 2016-04-03 paper.tex
Expand on Autechre.

The Kleene star is the set of all possible strings built from a set of elements. Here is a function that takes a set of
elements and produces an enumeration of the Kleene star of the set as a lazy sequence.

@@

\section{Anti}

A notorious example. The British government of the time wished to discourage rave culture, so it passed legislation that banned
music with "repetitive beats"?????. Autechre responded with a track in which every bar features a unique beat?????.

@@

'Blurred Lines' is a pop song that was written by Pharrell Williams and Robin Thicke. In March 2015,
they were found to have infringed on the copyright of the Marvin Gaye song 'Got to Give It Up'.

As a response to this situation, I decided to compose a track that would infringe on the copyright of both songs. The following
piece decodes the Champernowne word into music of three parts.

@@

What's more, every other song is also somewhere in there. Past, present and future.

>>>>

The Kleene star is the set of all possible strings built from a set of elements. Here is a function that takes a set of
elements and enumerates the Kleene star of that set as a lazy sequence.

@@

\section{Flutter}

The Criminal Justice and Public Order Act 1994 was an attempt by the UK Government to curb rave culture. The musicological
dilemma encountered by the government of the day was how to define raves. They settled on prohibiting gatherings where
"a succession of repetitive beats" were played.

The duo Autechre responded with the Anti EP, whose third track 'Flutter', was designed to protest the legislation. Band member
Sean Booth explained that they "made as many different bars as we could on the drum machine, then strung them all together."
In other words, as every bar features a unique beat, 'Flutter' does not match the government's algomusicological description
of "repetitive beats".

Autechre appreciated the practical difficulties of negotiating the subtleties of complexity theory at 3am in a field,
so they advised DJs to "have a lawyer and a musicologist present at all times to confirm the non repetitive nature of the
music in the event of police harassment."

Both legislators and artists are clearly taking algomusicological positions. The government attempted to construct the set
of all rave musics using a complexity characterisation. Autechre responded with what amounts to a diagonal argument, demonstrating
the inadequacy of the original claim.

@@

'Blurred Lines' is a 2013 pop song written by Pharrell Williams and Robin Thicke. In March 2015,
they were found to have infringed on the copyright of the Marvin Gaye song 'Got to Give It Up'.

Such judgements are perilous from a musicological point of view, as they are often based on a jury's intuition as to
the similarity between songs and not, for example, on a conditional Kolmogorov complexity analysis of the distance between
the two compositions.

As a response to this situation, I decided to compose a track that would infringe on the copyright of both songs. The following
piece decodes the Champernowne word into music.

@@

What's more, every other song is also somewhere in there. Past, present and future compositions already exist somewhere in
the depths of this infinite piece.
